\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts

\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{url}

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\begin{document}

\title{Your Paper Title Here}

\author{
\IEEEauthorblockN{First Author}
\IEEEauthorblockA{
\textit{Affiliation} \\
City, Country \\
email@example.com
}
}

\maketitle

\begin{abstract}
This is a placeholder abstract. Replace it with a concise summary of your
problem, method, key results, and contribution.
\end{abstract}

\begin{IEEEkeywords}
keyword one, keyword two, keyword three, keyword four
\end{IEEEkeywords}

\section{Introduction}
The introduction will be completed after the citation support bank and the
compact related-work argument are finalized. A temporary placeholder citation
is retained only to keep the BibTeX build valid before verified references are
added \cite{placeholder_article}.

\section{Problem Formulation}
Consider a local on-ramp merging decision at a planning instant. The target
mainline lane contains longitudinal vehicle positions
\(X=[x_1,\ldots,x_N]\), sorted in increasing order, and the merging vehicle
(MV) is located at \(x_m(0)\). Mainline vehicles are initially assumed to travel
at a reference speed \(v_{ref}\). The planner evaluates the candidate gaps
formed by adjacent target-lane vehicles. The \(i\)-th candidate gap is
\begin{equation}
    \mathrm{gap}_i=[x_{r,i},x_{f,i}],\quad
    G_i=x_{f,i}-x_{r,i},\quad
    c_i=\frac{x_{r,i}+x_{f,i}}{2},
    \label{eq:gap_definition}
\end{equation}
where \(x_{r,i}\) and \(x_{f,i}\) denote the rear and front boundary vehicles,
respectively, \(G_i\) is the current gap length, and \(c_i\) is the current
gap center.

Two safety lengths are distinguished. The required merging gap for inserting
the MV is
\begin{equation}
    G^{\mathrm{req}}=2D_h+l_m,
    \label{eq:required_gap}
\end{equation}
where \(D_h\) is the longitudinal safety headway and \(l_m\) is the MV length.
The adjacent-gap protection threshold is
\begin{equation}
    G^{\mathrm{adj}}=D_h+l_m.
    \label{eq:adjacent_gap}
\end{equation}
The former specifies the target gap size needed for a safe merge, while the
latter prevents boundary-vehicle cooperation from compressing neighboring
mainline gaps below a safety margin. Therefore, a candidate gap is not removed
only because \(G_i<G^{\mathrm{req}}\). Instead, its required shortage is
\begin{equation}
    \Delta_i=\max(0,G^{\mathrm{req}}-G_i).
    \label{eq:gap_shortage}
\end{equation}

The cooperation adjustment of candidate gap \(i\) is described by two
nonnegative quantities: \(\delta_{f,i}\), the forward displacement of the
front boundary vehicle, and \(\delta_{r,i}\), the backward displacement of the
rear boundary vehicle. These adjustments enlarge the target gap by
\(\delta_{f,i}+\delta_{r,i}\), but they also consume neighboring-gap margins
and thus are treated as bounded and costly mainline cooperation. The method
therefore estimates, for each candidate gap, a minimum necessary mainline
cooperation cost \(C_i^{\mathrm{coop}}\) and an MV ego merging cost
\(C_i^{\mathrm{ego}}\). The selected developed gap minimizes the integrated
valuation
\begin{equation}
    J_i=w_c C_i^{\mathrm{coop}}+w_e C_i^{\mathrm{ego}},
    \label{eq:abstract_score}
\end{equation}
subject to gap safety, neighboring-gap capacity, and MV kinematic constraints,
including
\begin{equation}
    v_{\min}\leq v_m(t)\leq v_{\max},\qquad
    a_{\min}\leq a_m(t)\leq a_{\max}.
\end{equation}

This formulation focuses on a single MV at one merging decision instant. The
target-lane positions are assumed to be available from perception,
communication, or the experimental scenario, and the boundary vehicles of a
candidate gap are assumed to be cooperative CAVs. A basic kinematic reachability
check may be applied before valuation to avoid physically unreachable gaps, but
reachability is only a screening condition in this paper. Multi-MV rolling
coordination, stochastic traffic generation, mixed CAV/HDV response, lane-change
gap supply, and closed-loop traffic simulation are outside the scope of the
present ICUS formulation.

\section{Mainline-Disturbance-Aware Cooperative Gap Development}
The proposed planner decomposes the local problem into four steps. First, it
computes how much each boundary vehicle can safely contribute while preserving
adjacent gaps. Second, it estimates the minimum necessary adjustment for each
candidate gap through a space-sensitive convex problem. Third, it scores all
developed candidates by combining mainline cooperation cost and MV ego cost.
Finally, it executes only the selected developed gap by generating the boundary
adjustment and the MV trajectory.

\subsection{Adjacent-Gap-Preserving Cooperation Capacity}
For an interior candidate gap \(\mathrm{gap}_i=[x_i,x_{i+1}]\), the adjacent
mainline gaps are \(G_{i-1}=x_i-x_{i-1}\) and
\(G_{i+1}=x_{i+2}-x_{i+1}\). When the front boundary vehicle moves forward, it
compresses the front-side neighboring gap. When the rear boundary vehicle moves
backward, it compresses the rear-side neighboring gap. Hence, the maximum safe
cooperation capacities are defined as
\begin{equation}
    \bar{\delta}_{f,i}=\max(0,G_{i+1}-G^{\mathrm{adj}}),
    \qquad
    \bar{\delta}_{r,i}=\max(0,G_{i-1}-G^{\mathrm{adj}}).
    \label{eq:capacity}
\end{equation}
These bounds are state-dependent: a boundary vehicle can contribute more only
when the adjacent gap on its outside has sufficient residual margin.

Candidate gap \(i\) can be developed into a safe merging gap by longitudinal
boundary-vehicle cooperation only if
\begin{equation}
    \bar{\delta}_{f,i}+\bar{\delta}_{r,i}\geq \Delta_i.
    \label{eq:coop_feasibility}
\end{equation}
The cooperatively developable set is then
\begin{equation}
    \mathcal{G}_{\mathrm{coop}}
    =
    \left\{
    i\,\middle|\,
    \bar{\delta}_{f,i}+\bar{\delta}_{r,i}\geq \Delta_i
    \right\}.
    \label{eq:coop_set}
\end{equation}
If \(\Delta_i=0\), the current gap already satisfies the required merging
length and the minimum cooperation estimate is
\(\delta_{f,i}^*=\delta_{r,i}^*=0\).

\subsection{Space-Sensitive Minimum-Disturbance Adjustment}
For a developable candidate gap with \(\Delta_i>0\), the shortage should be
allocated to the two boundary vehicles with minimum mainline disturbance. The
space-sensitive weights are
\begin{equation}
    \gamma_{f,i}
    =
    \left(\frac{\delta_{ref}}{\bar{\delta}_{f,i}}\right)^q,
    \qquad
    \gamma_{r,i}
    =
    \left(\frac{\delta_{ref}}{\bar{\delta}_{r,i}}\right)^q,
    \label{eq:gamma}
\end{equation}
for positive capacities. A smaller residual neighboring-gap margin leads to a
larger weight, so the optimization naturally avoids consuming the tighter side.
The candidate-level cooperation estimate is obtained from
\begin{align}
    \min_{\delta_{f,i},\delta_{r,i}}\quad
    C_i^{\mathrm{coop}}
    &=
    \gamma_{f,i}\delta_{f,i}^2+
    \gamma_{r,i}\delta_{r,i}^2
    \label{eq:coop_qp}\\
    \mathrm{s.t.}\quad
    \delta_{f,i}+\delta_{r,i}&\geq \Delta_i, \notag\\
    0\leq \delta_{f,i}&\leq \bar{\delta}_{f,i}, \notag\\
    0\leq \delta_{r,i}&\leq \bar{\delta}_{r,i}. \notag
\end{align}
Because the objective increases with the adjustment magnitudes, the optimum
satisfies \(\delta_{f,i}+\delta_{r,i}=\Delta_i\). Thus, the two-dimensional
problem admits a one-dimensional projected solution. Define
\begin{equation}
    L_i=\max(0,\Delta_i-\bar{\delta}_{r,i}),\qquad
    U_i=\min(\bar{\delta}_{f,i},\Delta_i),
    \label{eq:projection_bounds}
\end{equation}
and the unconstrained weighted split
\begin{equation}
    \delta_{f,i}^{\mathrm{raw}}
    =
    \frac{\gamma_{r,i}}{\gamma_{f,i}+\gamma_{r,i}}\Delta_i.
    \label{eq:raw_split}
\end{equation}
With \(\Pi_{[L_i,U_i]}(\cdot)\) denoting projection onto
\([L_i,U_i]\), the closed-form estimate is
\begin{equation}
    \delta_{f,i}^*
    =
    \Pi_{[L_i,U_i]}(\delta_{f,i}^{\mathrm{raw}}),
    \qquad
    \delta_{r,i}^*
    =
    \Delta_i-\delta_{f,i}^*.
    \label{eq:projected_solution}
\end{equation}
These quantities are candidate-level estimates used for valuation; no physical
adjustment is applied before the best developed gap is selected.

\subsection{Disturbance-Efficiency Valuation for Developed Gaps}
The adjustment estimate shifts the center of the developed candidate gap by
\begin{equation}
    \Delta c_i=\frac{\delta_{f,i}^*-\delta_{r,i}^*}{2}.
    \label{eq:center_shift}
\end{equation}
Consequently, the MV must match the terminal displacement
\begin{equation}
    d_i=c_i+\frac{\delta_{f,i}^*-\delta_{r,i}^*}{2}-x_m(0).
    \label{eq:terminal_displacement}
\end{equation}
If the front boundary contributes more, the developed gap center moves forward;
if the rear boundary contributes more, the developed gap center moves backward.
This center shift links mainline cooperation to the MV ego trajectory cost.

For each developed candidate, the cooperation cost is
\begin{equation}
    C_i^{\mathrm{coop}}
    =
    \gamma_{f,i}(\delta_{f,i}^*)^2+
    \gamma_{r,i}(\delta_{r,i}^*)^2.
    \label{eq:coop_cost}
\end{equation}
Using the terminal time rule in the next subsection, the MV ego cost is
\begin{equation}
    C_i^{\mathrm{ego}}
    =
    \frac{K d_i^2}{(t_{m,i}^*)^3}
    +
    w_t t_{m,i}^*,
    \qquad
    K=\frac{120}{7}.
    \label{eq:ego_cost}
\end{equation}
The disturbance-efficiency score is
\begin{equation}
    J_i
    =
    w_c C_i^{\mathrm{coop}}
    +
    w_e C_i^{\mathrm{ego}}.
    \label{eq:valuation}
\end{equation}
The best developed gap is selected by
\begin{equation}
    i^*
    =
    \underset{i\in\mathcal{G}_{\mathrm{coop}}}{\arg\min}\;J_i.
    \label{eq:selected_gap}
\end{equation}
The order is important: all candidates are first estimated and scored, then
\(i^*\) is selected, and only the selected gap is executed.

\subsection{Terminal Time, Merging Location, and Feasible Trajectory}
The candidate terminal time is computed from a fifth-order smooth transition
\begin{equation}
    S(\tau)=10\tau^3-15\tau^4+6\tau^5,\qquad
    \tau=\frac{t}{t_m},
    \label{eq:smooth_function}
\end{equation}
which satisfies zero relative velocity and acceleration at both ends. The
unconstrained energy-time tradeoff gives
\begin{equation}
    t_{m,i}^{0}
    =
    \left(\frac{3K d_i^2}{w_t}\right)^{1/4}.
    \label{eq:t_unconstrained}
\end{equation}
Let \(a_{\lim}=\min(a_{\max},|a_{\min}|)\). Since
\(\max_{\tau\in[0,1]}|S''(\tau)|=10/\sqrt{3}\), the acceleration constraint
requires
\begin{equation}
    t_{a,i}
    =
    \sqrt{
    \frac{\frac{10}{\sqrt{3}}|d_i|}{a_{\lim}}
    }.
    \label{eq:t_acc}
\end{equation}
The velocity constraint uses \(S'_{\max}=1.875\), yielding
\begin{equation}
    t_{v,i}
    =
    \begin{cases}
    \dfrac{1.875|d_i|}{v_{\max}-v_{ref}}, & d_i\geq 0,\\[8pt]
    \dfrac{1.875|d_i|}{v_{ref}-v_{\min}}, & d_i<0.
    \end{cases}
    \label{eq:t_vel}
\end{equation}
The final candidate terminal time and merging location are
\begin{equation}
    t_{m,i}^*
    =
    \max(t_{m,i}^{0},t_{a,i},t_{v,i}),
    \qquad
    p_{m,i}=x_m(0)+v_{ref}t_{m,i}^*+d_i.
    \label{eq:terminal_time_location}
\end{equation}

After \(i^*\) is selected, define
\begin{align}
    d^*&=d_{i^*},&
    t_m^*&=t_{m,i^*}^*,&
    p_m^*&=p_{m,i^*}, \notag\\
    \delta_f^*&=\delta_{f,i^*}^*,&
    \delta_r^*&=\delta_{r,i^*}^*. \label{eq:selected_quantities}
\end{align}
For \(0\leq t\leq t_m^*\), the MV trajectory is
\begin{align}
    x_m(t)
    &=
    x_m(0)+v_{ref}t+
    d^*S\left(\frac{t}{t_m^*}\right), \label{eq:mv_position}\\
    v_m(t)
    &=
    v_{ref}
    +
    \frac{d^*}{t_m^*}
    S'\left(\frac{t}{t_m^*}\right), \label{eq:mv_velocity}\\
    a_m(t)
    &=
    \frac{d^*}{(t_m^*)^2}
    S''\left(\frac{t}{t_m^*}\right). \label{eq:mv_acc}
\end{align}
The selected rear and front boundary vehicles follow
\begin{align}
    x_r(t)
    &=
    x_r^*+v_{ref}t-
    \delta_r^*S\left(\frac{t}{t_m^*}\right), \label{eq:rear_traj}\\
    x_f(t)
    &=
    x_f^*+v_{ref}t+
    \delta_f^*S\left(\frac{t}{t_m^*}\right), \label{eq:front_traj}
\end{align}
where \(x_r^*=x_{r,i^*}\) and \(x_f^*=x_{f,i^*}\). Therefore, the selected
gap length evolves as
\begin{equation}
    G^*(t)
    =
    G_{i^*}
    +
    (\delta_f^*+\delta_r^*)
    S\left(\frac{t}{t_m^*}\right),
    \label{eq:dynamic_gap}
\end{equation}
and at the terminal time
\begin{equation}
    G^*(t_m^*)=G_{i^*}+\delta_f^*+\delta_r^*
    \geq G^{\mathrm{req}}.
    \label{eq:terminal_gap}
\end{equation}
The developed gap center is
\begin{equation}
    c^*(t)
    =
    c_{i^*}+v_{ref}t+
    \frac{\delta_f^*-\delta_r^*}{2}
    S\left(\frac{t}{t_m^*}\right),
    \label{eq:dynamic_center}
\end{equation}
so \(c^*(t_m^*)=p_m^*\). Thus, the selected developed gap is converted into a
terminal time, terminal position, and feasible MV trajectory while maintaining
the required developed gap length.

\section{Experiments}
The experiments section will be drafted after the S01 candidate evaluation
table, capacity-ablation table, and representative FIFO comparison data are
assembled.

\section{Conclusion}
The conclusion will be completed after the method and experimental evidence are
fully aligned.

\section*{Acknowledgment}
If you do not need acknowledgments or funding information, you can delete this
section before submission.

\bibliographystyle{IEEEtran}
\bibliography{refs}

\end{document}
